Differential Expression - MSSM-Penn-Pitt - DLPFC - Sex

### 2020-07-31 individual-cohorts/MSSM-Penn-Pitt_DLPFC_DE.Rmd
Test Sex with Dx added to the model

# Set covariates to adjust for from model selection
adjust.covars <- c("Sex", "ageOfDeath", "RIN2", "RIN", "IntronicRate", "IntragenicRate")
random_effect <- c("Institution")
```

>>>>

# Set covariates to adjust for from model selection
adjust.covars <- c("Sex", "Dx", "ageOfDeath", "RIN2", "RIN", "IntronicRate", "IntragenicRate")
random_effect <- c("Institution")
```
